---
title: "LMM_Electronics"
author: "Go young hee"
date: '2021 2 9 '
output: html_document
---

## install package
```{r}
#getwd()
library(data.table)
library(dplyr)
library(olsrr)
library(lme4)
library(ggplot2)
```


## data load
```{r}
df<-fread("train_eda_fin.csv")
head(df)
```

## data Preprocessing
```{r}
df_el<-df%>%subset(category_1=="Electronics")
head(df_el)
```

## modeling

#### 1. Category_2

1.1 fixed effect
  
  - no random effect = linear regression, Exclude Category2 variable
```{r}
cate2_aic1<-lm(formula=log_price~item_condition_id+shipping,data=df_el)%>%AIC()
print(cate2_aic1) # 127450.3
```

  - no random effect ,Category2 is the fixed effect
  - increase dimension : Category2 as a factor
```{r}
cate2_aic2<-lm(formula=log_price~item_condition_id+shipping+category_2,data=df_el)%>%AIC()
print(cate2_aic2) # 123349.8
```

1.2 random effect
  
  - random intercept: category2
```{r}
cate2_aic3<-lmer(formula=log_price~item_condition_id+shipping+(1|category_2),data=df_el)%>%AIC()
print(cate2_aic3) # 123405.3
```

  - random intercept + random slope (item_condition_id)
```{r}
cate2_aic4<-lmer(formula=log_price~item_condition_id+shipping+(item_condition_id|category_2),data=df_el)%>%AIC()

print(cate2_aic4) # 121357.5
```

  - random intercept + random slope(Shipping)
```{r}
cate2_aic5<-lmer(formula=log_price~item_condition_id+shipping+(shipping|category_2),data=df_el)%>%AIC()

print(cate2_aic5) # 122907.7
```

#### 2. category3

2.1 fixed effect
  - no random effect = linear regression, Exclude Category3 variable
  - It is same on 1.1 fixed effect
```{r}
cate3_aic1<-lm(formula=log_price~item_condition_id+shipping,data=df_el)%>%AIC()
print(cate3_aic1) # 127450.3
```

  - no random effect ,Category3 is the fixed effect
  - increase dimension : Category3 as a factor
```{r}
cate3_aic2<-lm(formula=log_price~item_condition_id+shipping+category_3,data=df_el)%>%AIC()
print(cate3_aic2) # 105427.5
```

2.2 random effect
  
  - random intercept: category3
```{r}
cate3_aic3<-lmer(formula=log_price~item_condition_id+shipping+(1|category_3),data=df_el)%>%AIC()
print(cate3_aic3) # 105613.1
```
  - random intercept + random slope (item_condition_id)
```{r}
cate3_aic4<-lmer(formula=log_price~item_condition_id+shipping+(item_condition_id|category_3),data=df_el)%>%AIC()

print(cate3_aic4) # 104258.4
```


  - random intercept + random slope(Shipping)
```{r}
cate3_aic5<-lmer(formula=log_price~item_condition_id+shipping+(shipping|category_3),data=df_el)%>%AIC()

print(cate3_aic5) # 105177
```


# compare the models 
```{r}

cate2_aic<-c(cate2_aic1,cate2_aic2,cate2_aic3,cate2_aic4,cate2_aic5)
print(cate2_aic)

cate3_aic<-c(cate3_aic1,cate3_aic2,cate3_aic3,cate3_aic4,cate3_aic5)
print(cate3_aic)
```

  - Visualization
```{r}
aic_df<-data.frame(value=c(cate2_aic,cate3_aic),
                   random.effect=c(rep('category2',5),rep('category3',5)),
                   model=rep(c('model1','model2','model3','model4','model5'),2))
nrow(aic_df)
aic_df

p1<-ggplot(data=aic_df,aes(x=model,y=value,color=random.effect,group=random.effect))+
  geom_line(aes(linetype=random.effect))+
  geom_point(size=3)+ # alpha는 투명도 조절
  theme(axis.text.x=element_text(angle=45,vjust=1,hjust=1))+
  ylab("AIC")+
  scale_colour_grey(start=0.7, end=0.3)
p1
#ggsave("0. model compare.png",p1,scale=0.8)
```

# Final model

```{r}
model<-lmer(formula=log_price~item_condition_id+shipping+(item_condition_id|category_3),data=df_el)
summary(model)
```